Minimizing Time Required For Graduation

### 2010-12-04 paper.tex
Fixed some of the references and scaled the graph figure by 0.5

\section{Introduction} \subsection{Background} Registration can be a stressful
time for every student at the University of Washington. Without deliberate
planning, students must decide which classes to take on a quarterly basis. The
decision process involves considering many factors, such as quarterly class
offerings, the amount of credits, the prerequisites of the classes, time
conflicts, and how the choices in current quarter affect future quarters. The
University of Washington registration system provides a schedule finder;
however, it only takes into account time conflicts, and does not give advice on
how to pick the most ideal schedule. The situation described above makes it
difficult for students advising faculties. A student's graduation time may be
extended because of his or her inability to take a class that has limited
offerings during that particular year, for reasons such as not satisfying the
prerequisites of the class. The advising office’s workload can also be increased
due to the changing plans and majors of students and their need for repeated
advising.

@@

\subsection{Selection of Quarterly Classes} \subsubsection{Selection Procedure}
At this point in time, we know which course offerings are available for the
given student to register for, and we must now pick the most optimal ones. There
a several ways we could view the problem of determining which classes to take
each quarter. We will initially encode the class selection as a binary integer
programming problem in spirit of the methods presented by Dinkel et al
\cite{dinel:scheduling}. and Pritsker et al \cite{prisker:informs}. At this
point we have the set $L$ containing possible classes we that we need to take.

@@

\includegraphics{more_prereq_tree}

@@

\bibliography{references}{} \bibliographystyle{plain} \end{document}

>>>>

\section{Introduction} \subsection{Background} Registration can be a stressful
time for every student at the University of Washington. Without deliberate
planning, students must decide which classes to take on a quarterly basis. The
decision process involves considering factors such as quarterly class
offerings, the amount of credits, the prerequisites of the classes, time
conflicts, and how the choices in current quarter affect future quarters. The
University of Washington registration system provides a schedule finder;
however, it only takes into account time conflicts, and does not give advice on
how to pick the most ideal schedule. The situation described above makes it
difficult for students advising faculties. A student's graduation time may be
extended because of his or her inability to take a class that has limited
offerings during that particular year, for reasons such as not satisfying the
prerequisites of the class. The advising office’s workload can also be increased
due to the changing plans and majors of students and their need for repeated
advising.

@@

\subsection{Selection of Quarterly Classes} \subsubsection{Selection Procedure}
At this point in time, we know which course offerings are available for the
given student to register for, and we must now pick the most optimal ones. There
a several ways we could view the problem of determining which classes to take
each quarter. We will initially encode the class selection as a binary integer
programming problem in spirit of the methods presented by Dinkel et al
\cite{dinkel:scheduling}. and Pritsker et al \cite{prisker:informs}. At this
point we have the set $L$ containing possible classes we that we need to take.

@@

\includegraphics[scale=0.5]{more_prereq_tree}

@@

\bibliography{paper_references}{} \bibliographystyle{plain} \end{document}
